                             %% ut-thesis.tex -- document template for graduate theses at UofT
%%
%% Copyright (c) 1998-2012 Francois Pitt <fpitt@cs.utoronto.ca>
%% last updated at 09:43 (EDT) on Fri  1 Jun 2012
%%
%% This work may be distributed and/or modified under the conditions of
%% the LaTeX Project Public License, either version 1.3c of this license
%% or (at your option) any later version.
%% The latest version of this license is in
%%     http://www.latex-project.org/lppl.txt
%% and version 1.3c or later is part of all distributions of LaTeX
%% version 2005/12/01 or later.
%%
%% This work has the LPPL maintenance status "maintained".
%%
%% The Current Maintainer of this work is
%% Francois Pitt <fpitt@cs.utoronto.ca>.
%%
%% This work consists of the files listed in the accompanying README.

%% SUMMARY OF FEATURES:
%%
%% All environments, commands, and options provided by the `ut-thesis'
%% class will be described below, at the point where they should appear
%% in the document.  See the file `ut-thesis.cls' for more details.
%%
%% To explicitly set the pagestyle of any blank page inserted with
%% \cleardoublepage, use one of \clearemptydoublepage,
%% \clearplaindoublepage, \clearthesisdoublepage, or
%% \clearstandarddoublepage (to use the style currently in effect).
%%
%% For single-spaced quotes or quotations, use the `longquote' and
%% `longquotation' environments.


%%%%%%%%%%%%         PREAMBLE         %%%%%%%%%%%%

%%  - Default settings format a final copy (single-sided, normal
%%    margins, one-and-a-half-spaced with single-spaced notes).
%%  - For a rough copy (double-sided, normal margins, double-spaced,
%%    with the word "DRAFT" printed at each corner of every page), use
%%    the `draft' option.
%%  - The default global line spacing can be changed with one of the
%%    options `singlespaced', `onehalfspaced', or `doublespaced'.
%%  - Footnotes and marginal notes are all single-spaced by default, but
%%    can be made to have the same spacing as the rest of the document
%%    by using the option `standardspacednotes'.
%%  - The size of the margins can be changed with one of the options:
%%     . `narrowmargins' (1 1/4" left, 3/4" others),
%%     . `normalmargins' (1 1/4" left, 1" others),
%%     . `widemargins' (1 1/4" all),
%%     . `extrawidemargins' (1 1/2" all).
%%  - The pagestyle of "cleared" pages (empty pages inserted in
%%    two-sided documents to put the next page on the right-hand side)
%%    can be set with one of the options `cleardoublepagestyleempty',
%%    `cleardoublepagestyleplain', or `cleardoublepagestylestandard'.
%%  - Any other standard option for the `report' document class can be
%%    used to override the default or draft settings (such as `10pt',
%%    `11pt', `12pt'), and standard LaTeX packages can be used to
%%    further customize the layout and/or formatting of the document.

%% *** Add any desired options. ***
\documentclass[doublespaced, 12pt]{ut-thesis}
\usepackage{natbib}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{caption}
\usepackage{amsmath}

%
\usepackage{multirow}
\usepackage{subfig}
\usepackage{lipsum}                    
\usepackage{xargs}                     
\usepackage{graphicx}
\usepackage{paralist}
\usepackage[capitalise]{cleveref}
% \usepackage[utf8]{inputenc}
% \usepackage[T1]{fontenc}
\graphicspath{ {images/} }
\usepackage[pdftex,dvipsnames]{xcolor} 
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}

\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\chapref}[1]{Chapter \ref{#1}}


\newcommand{\limit}[0]{\textrm{limit}}

%% *** Add \usepackage declarations here. ***
%% The standard packages `geometry' and `setspace' are already loaded by
%% `ut-thesis' -- see their documentation for details of the features
%% they provide.  In particular, you may use the \geometry command here
%% to adjust the margins if none of the ut-thesis options are suitable
%% (see the `geometry' package for details).  You may also use the
%% \setstretch command to set the line spacing to a value other than
%% single, one-and-a-half, or double spaced (see the `setspace' package
%% for details).


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                    %%
%%                   ***   I M P O R T A N T   ***                    %%
%%                                                                    %%
%%  Fill in the following fields with the required information:       %%
%%   - \degree{...}       name of the degree obtained                 %%
%%   - \department{...}   name of the graduate department             %%
%%   - \gradyear{...}     year of graduation                          %%
%%   - \author{...}       name of the author                          %%
%%   - \title{...}        title of the thesis                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% *** Change this example to appropriate values. ***
\degree{Master of Science}
\department{Computer Science}
\gradyear{2016}
\author{Priya Sidhaye}
\title{Examining Indicative Tweet Generation As An Extractive Summarization Problem}
\frenchtitle{temp}

%% *** NOTE ***
%% Put here all other formatting commands that belong in the preamble.
%% In particular, you should put all of your \newcommand's,
%% \newenvironment's, \newtheorem's, etc. (in other words, all the
%% global definitions that you will need throughout your thesis) in a
%% separate file and use "\input{filename}" to input it here.


%% *** Adjust the following settings as desired. ***

%% List only down to subsections in the table of contents;
%% 0=chapter, 1=section, 2=subsection, 3=subsubsection, etc.
\setcounter{tocdepth}{2}

%% Make each page fill up the entire page.
\flushbottom


%%%%%%%%%%%%      MAIN  DOCUMENT      %%%%%%%%%%%%

\begin{document}

%% This sets the page style and numbering for preliminary sections.
\begin{preliminary}

%% This generates the title page from the information given above.
\maketitle

%% There should be NOTHING between the title page and abstract.
%% However, if your document is two-sided and you want the abstract
%% _not_ to appear on the back of the title page, then uncomment the
%% following line.
%\cleardoublepage

%% This generates the abstract page, with the line spacing adjusted
%% according to SGS guidelines.
\begin{abstract}
%% *** Put your Abstract here. ***
%% (At most 150 words for M.Sc. or 350 words for Ph.D.)

Social media such as Twitter have become an important method of communication, with potential opportunities for Natural Language Generation (NLG) to facilitate the generation of social media content. The presence of the URL in the short tweet is a strong signal that the tweet is functioning to help Twitter users decide whether to read the full article. We focus on the generation of these \emph{indicative tweets}, which we define as tweets containing links to external web pages. Extractive summarization is the process of generating a summary of the text by choosing a subset of words from the text. Previous work in automatic tweet generation has viewed the linked web page as the source text from which the tweet is generated in an extractive summarization setting. However, this setting may not be appropriate, because it is unclear to what extent indicative tweets actually behave like extractive summaries.

We collect a corpus of indicative tweets with their associated articles and investigate the extent to which they can be derived from the articles using extractive methods. We also consider the impact of the formality and genre of the article. We conduct further studies to detect the \textit{function} of the tweet, i.e., the reason the user shared the tweet. In particular, with the aim of finding possible factors that influence the composition of the tweet, we considered whether the tweet is an advertisement or summary of the article. We find a significant positive correlation between the degree of extraction and the degree to which a tweet behaves like a summary. 

Our results demonstrate the limits of viewing indicative tweet generation as extractive summarization, and point to the need for the development of methods for tweet generation that are not based on simple extractive techniques. We also show the need for genre-sensitive methods for generating tweets.

This thesis contributes a novel dataset of indicative tweets labelled by their function as defined above. The tweets are  categorized by their subjects, and span broad areas of public interest.  In terms of theoretical contributions, this thesis clarifies the relationship between an indicative tweet and the article to which it relates and lays the groundwork for developing a system that would be able to generate indicative tweets from referenced documents, possibly based on parameters such as whether the tweet is intended to be an advertisement or a public service announcement.

\end{abstract}
\begin{frenchabstract}
Les r\'{e}seaux  sociaux tels que Twitter sont devenus un moyen de communication important, soulignant de plus en plus de possibilit\'{e}s de g\'{e}n\'{e}ration automatique de texte (NLG) pour faciliter la g\'{e}n\'{e}ration des textes qu'on rencontre dans les r\'{e}seaux  sociaux. Nous nous concentrons sur la g\'{e}n\'{e}ration de \textit{tweets indicatifs} qu'on d\'{e}finit comme \'{e}tant des tweets contenant un lien pointant vers de pages web externes. Le r\'{e}sum\'{e} automatique par extraction consiste \`{a} g\'{e}n\'{e}rer un r\'{e}sum\'{e} du texte en s\'{e}lectionnant certains mots de ce texte. Les approches ant\'{e}rieures \`{a} la g\'{e}n\'{e}ration automatique de tweets ont consid\'{e}r\'{e} que la page web li\'{e}e est la source \`{a} partir de laquelle le tweet est g\'{e}n\'{e}r\'{e} dans un cadre de r\'{e}sum\'{e} automatique par extraction. Toutefois, ce cadre-l\`{a} pourrait ne pas \^{e}tre le plus convenable puisqu'il n'est pas assez \'{e}vident dans quelle mesure les tweets indicatifs se comportent comme \'{e}tant des r\'{e}sum\'{e}s par extraction.

Nous collectons un corpus de tweets indicatifs avec leurs articles associ\'{e}s et \'{e}tudions dans quelle mesure ils peuvent être obtenus \`{a} partir des articles en utilisant des m\'{e}thodes de r\'{e}sum\'{e} automatique par extraction. Nous consid\'{e}rons \'{e}galement l'effet de la formalit\'{e} et le genre de l'article. Nous menons des \'{e}tudes pour sp\'{e}cifier et mieux comprendre la \textit{fonction} du tweet, c'est-\`{a}-dire, la raison pour laquelle l'utilisateur a partag\'{e} le tweet. Particuli\`{e}rement, dans le but de trouver les facteurs qui agissent sur la composition du tweet, nous consid\'{e}rons si le tweet est une annonce publique ou un r\'{e}sum\'{e} de l'article. Nous trouvons une corr\'{e}lation positive consid\'{e}rable entre le degr\'{e} d'extraction et le degr\'{e} selon lequel le tweet se comporte comme \'{e}tant un r\'{e}sum\'{e}. Nos r\'{e}sultats d\'{e}montrent les limites de consid\'{e}rer la g\'{e}n\'{e}ration des tweets indicatifs comme \'{e}tant une m\'{e}thode de r\'{e}sum\'{e} automatique par extraction. Ils soulignent \'{e}galement le besoin de d\'{e}velopper de m\'{e}thodes de g\'{e}n\'{e}ration de tweets qui ne sont pas bas\'{e}es sur de simples techniques d'extraction. Nous d\'{e}montrons de m\^{e}me le besoin de m\'{e}thodes de g\'{e}n\'{e}ration de tweets qui sont sensitives au genre.

Cette th\`{e}se pr\'{e}sente un nouvel ensemble de donn\'{e}es de tweets indicatifs que nous avons class\'{e} par leurs fonctions comme d\'{e}finies ci-dessus. Les tweets sont class\'{e}s par leurs sujets et couvrent de grands domaines d'int\'{e}r\^{e}t public. En tant que contribution th\'{e}orique, cette th\`{e}se clarifie la relation entre un tweet indicatif et l'article correspondant et pr\'{e}sente un plan pour le d\'{e}veloppement d'un syst\`{e}me qui pourrait g\'{e}n\'{e}rer des tweets indicatifs \`{a} partir de documents r\'{e}f\'{e}renc\'{e}s, en se basant sur de param\`{e}tres qui peuvent, par exemple, consid\'{e}rer si le tweet fonctionne comme une publicit\'{e} ou un message d'int\'{e}r\^{e}t public.


\end{frenchabstract}

\input{texfiles/ack}

%% Anything placed between the abstract and table of contents will
%% appear on a separate page since the abstract ends with \newpage and
%% the table of contents starts with \clearpage.  Use \cleardoublepage
%% for anything that you want to appear on a right-hand page.

%% This generates a "dedication" section, if needed
%% (uncomment to have it appear in the document).
%\begin{dedication}
%% *** Put your Dedication here. ***
%\end{dedication}

%% The `dedication' and `acknowledgements' sections do not create new
%% pages so if you want the two sections to appear on separate pages,
%% you should put an explicit \newpage between them.

%% This generates an "acknowledgements" section, if needed
%% (uncomment to have it appear in the document).
%\begin{acknowledgements}
%% *** Put your Acknowledgements here. ***
%\end{acknowledgements}

%% This generates the Table of Contents (on a separate page).
\tableofcontents

%% This generates the List of Tables (on a separate page), if needed
%% (uncomment to have it appear in the document).
\listoftables

%% This generates the List of Figures (on a separate page), if needed
%% (uncomment to have it appear in the document).
\listoffigures

%% You can add commands here to generate any other material that belongs
%% in the head matter (for example, List of Plates, Index of Symbols, or
%% List of Appendices).

%% End of the preliminary sections: reset page style and numbering.
\end{preliminary}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  Put your Chapters here; the easiest way to do this is to keep     %%
%%  each chapter in a separate file and `\include' all the files.     %%
%%  Each chapter file should start with "\chapter{ChapterName}".      %%
%%  Note that using `\include' instead of `\input' will make each     %%
%%  chapter start on a new page, and allow you to format only parts   %%
%%  of your thesis at a time by using `\includeonly'.                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% *** Include chapter files here. ***
\input{texfiles/intro}

\input{texfiles/relatedwork}


\input{texfiles/data}


\input{texfiles/analysis}


\input{texfiles/userstudy}


\input{texfiles/conclusion}


%% This adds a line for the Bibliography in the Table of Contents.
\addcontentsline{toc}{chapter}{Bibliography}
%% *** Set the bibliography style. ***
%% (change according to your preference/requirements)
\bibliographystyle{unsrtnat}
%% *** Set the bibliography file. ***
%% ("thesis.bib" by default; change as needed)
\bibliography{thesis}

%% *** NOTE ***
%% If you don't use bibliography files, comment out the previous line
%% and use \begin{thebibliography}...\end{thebibliography}.  (In that
%% case, you should probably put the bibliography in a separate file and
%% `\include' or `\input' it here).

\end{document}
